---
title: "ingest"
author: "JJayes"
date: "28/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(here)

```

### Read in data for orders

```{r}
df <- read_excel(here("data", "raw_orders.xlsx")) %>% janitor::clean_names()
```

### Investigate

```{r}
df <- df %>% 
  filter(!is.na(item))

df <- df %>% 
  mutate(index = case_when(
    item == "Produkt" ~ 1,
    TRUE ~ 0
  )) %>% 
  mutate(person = cumsum(index)) %>% 
  select(-index)

df <- df %>% 
  filter(!item %in% c("Produkt", "Totalt", "Midsummer Sittning dinner ticket (vegetarian)"))
```

### What is the budget?

```{r}
# revenue
revenue <- df %>% 
  filter(item %in% c("Dinner ticket (vegetarian)", "Alcohol package (includes 2 glasses of wine)", "After party ticket", "Dinner ticket (add-on) adding traditional swedish fish to the dinner")) %>% 
  mutate(price = str_replace_all(price, ",", "."),
         price = parse_number(price)) %>%
  summarise(sum(price)) 

revenue

# subsidized LE for us per person
30+330+60+60
# herring, after party, drinks, food
480*10

(480*10) + revenue %>% pull
```



```{r}
df <- df %>% 
  group_by(person) %>% 
  count(item, number) %>% 
  ungroup() %>% 
  select(-number) %>% 
  pivot_wider(names_from = item, values_from = n) %>% 
  janitor::clean_names()

df_info <- df
```

### Read in data for 

```{r}
df <- read_excel(here("data", "raw_names.xlsx")) %>% janitor::clean_names()

df <- df %>% 
  filter(!is.na(item))

df <- df %>% 
  mutate(index = case_when(
    item == "Namn" ~ 1,
    TRUE ~ 0
  )) %>% 
  mutate(person = cumsum(index)) %>% 
  select(-index)


df <- df %>% 
  filter(item %in% c("Namn", "Land", "E-post", "Mobiltelefon")) %>% 
  pivot_wider(names_from = item) %>% 
  janitor::clean_names()
```


### join

```{r}
df <- df %>% 
  inner_join(df_info)
```

### Add in committee and Damla

```{r}
df <- df %>% 
  bind_rows(read_excel(here("data", "df_committee.xlsx")))
```


### Making edits

Olivia Henriksson to fish

Madeleine Erikson to veggie

Oskar Andersson to fish


```{r}
df <- df %>% 
  mutate(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner = case_when(
    str_detect(namn, "Olivia  Henriksson") ~ 1,
    str_detect(namn, "Madeleine Erikson") ~ 0,
    str_detect(namn, "Oskar Andersson") ~ 1,
    TRUE ~ dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner
  ))


df %>% count(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner)

df %>% arrange(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner) %>% 
  select(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner) %>% 
  mutate(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner = as.character(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner)) %>%
  pull() %>% 
  writeClipboard()

```

```{r}



df %>% 
  write_excel_csv(here("data", "attendees.csv"))

df %>% filter(!is.na(snapsbiljett_maximum_2_person)) %>% 
  select(namn) %>% pull() %>% 
  writeClipboard()
```


### now what do we need?

- List for flower crowns
- List for seating chart based on nationality, then coloured based on food, drinks etc.
- Email MOP
- How many after party tickets can we sell?

## List for flower crowns

```{r}
df %>% 
  filter(midsummer_flower_crown != 0) %>% 
  select(namn, e_post, mobiltelefon) 
  # write.csv(here("data", "flower_crowns.csv"))
```

## Email MOP

```{r}
df %>% 
  count(alcohol_package_includes_2_glasses_of_wine)

df %>% 
  count(dinner_ticket_add_on_adding_traditional_swedish_fish_to_the_dinner)
```



```{r}
df %>% 
  count(land, sort = T)
```

### seating chart

```{r}
df %>% 
  count(after_party_ticket)
```


